### 2020-09-01 benchmarking/benchmarkingVM/ESS_timesettings.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:56
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 49.20,184.67) --
	(458.76,184.67);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 53.30,192.21) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 57.39,192.33) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 61.49,192.07) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 65.58,189.41) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 69.68,201.89) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 73.77,192.33) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 77.87,193.68) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 81.96,194.75) circle (  2.25);

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.30,193.62) --
	( 86.06,193.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 69.68,297.24) {5.2\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] ( 90.16,  0.00) --
	( 90.16,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 94.25,131.15) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 98.35,142.51) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (102.44,137.12) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (106.54,133.51) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (110.63,115.30) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (114.73,104.29) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (118.83,121.85) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (122.92, 87.01) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 94.25,122.43) --
	(127.02,122.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (110.63,297.24) {29\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (131.11,  0.00) --
	(131.11,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (135.21,210.25) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (139.30,199.78) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (143.40,200.44) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (147.49,195.49) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (151.59,212.96) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (155.69,234.21) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (159.78,210.45) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (163.88,228.46) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (135.21,211.98) --
	(167.97,211.98);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (151.59,297.24) {17\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (172.07,  0.00) --
	(172.07,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (176.16,137.47) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (180.26,147.34) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (184.36,140.19) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (188.45,140.07) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (192.55,140.34) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (196.64,103.65) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (200.74,122.50) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (204.83,113.14) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.16,131.17) --
	(208.93,131.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (192.55,297.24) {26\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (213.02,  0.00) --
	(213.02,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (217.12,221.94) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (221.22,222.13) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (225.31,218.65) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (229.41,207.34) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (233.50,217.59) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (237.60,198.68) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (241.69,213.67) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (245.79,189.78) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (217.12,211.56) --
	(249.88,211.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (233.50,297.24) {16\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.98,  0.00) --
	(253.98,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (258.08,229.80) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (262.17,227.84) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (266.27,228.47) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (270.36,216.45) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (274.46,237.37) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (278.55,221.39) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (282.65,219.64) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (286.75,212.76) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (258.08,224.38) --
	(290.84,224.38);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (274.46,297.24) {25\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (294.94,  0.00) --
	(294.94,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (299.03,243.36) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (303.13,239.88) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (307.22,240.25) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (311.32,228.38) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (315.41,250.89) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (319.51,247.98) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (323.61,232.84) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (327.70,224.69) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (299.03,238.74) --
	(331.80,238.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (315.41,297.24) {35\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (335.89,  0.00) --
	(335.89,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (339.99,133.85) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (344.08,146.75) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (348.18,141.24) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (352.28,140.02) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (356.37,135.64) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (360.47,103.87) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (364.56,119.49) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (368.66,109.12) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (339.99,129.36) --
	(372.75,129.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (356.37,297.24) {27\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (376.85,  0.00) --
	(376.85,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (380.94,141.02) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (385.04,149.13) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (389.14,142.97) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (393.23,139.61) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (397.33,137.57) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (401.42,114.39) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (405.52,129.13) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (409.61,140.48) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (380.94,137.06) --
	(413.71,137.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (397.33,297.24) {23\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (417.80,  0.00) --
	(417.80,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (421.90,147.24) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (426.00,156.87) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (430.09,147.29) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (434.19,143.53) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (438.28,144.92) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (442.38,124.70) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (446.47,142.61) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (450.57,147.18) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (421.90,144.49) --
	(454.67,144.49);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (438.28,297.24) {20\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (458.76,  0.00) --
	(458.76,357.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 69.68, 61.20) -- ( 69.68, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.63, 61.20) -- (110.63, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.59, 61.20) -- (151.59, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.55, 61.20) -- (192.55, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.50, 61.20) -- (233.50, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.46, 61.20) -- (274.46, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.41, 61.20) -- (315.41, 55.20);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:31:18
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 49.20,184.67) --
	(459.67,184.67);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 52.93,182.48) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 56.66,177.12) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 60.39,177.00) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 64.13,177.26) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 67.86,179.92) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 71.59,167.44) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 75.32,177.00) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 79.05,175.65) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] ( 82.78,174.58) circle (  2.25);

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 52.93,176.54) --
	( 86.52,176.54);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 69.72,297.24) {4.5\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] ( 90.25,  0.00) --
	( 90.25,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 93.98,212.46) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 97.71,238.18) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (101.44,226.82) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (105.17,232.21) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (108.90,235.82) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (112.64,254.03) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (116.37,265.04) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (120.10,247.48) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (123.83,282.32) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 93.98,244.94) --
	(127.56,244.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (110.77,297.24) {40\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (131.29,  0.00) --
	(131.29,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (135.03,179.49) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (138.76,159.08) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (142.49,169.55) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (146.22,168.89) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (149.95,173.84) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (153.68,156.37) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (157.42,135.12) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (161.15,158.88) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (164.88,140.87) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (135.03,160.77) --
	(168.61,160.77);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (151.82,297.24) {13\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (172.34,  0.00) --
	(172.34,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (176.07,216.47) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (179.80,231.86) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (183.54,221.99) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (187.27,229.14) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (191.00,229.26) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (194.73,228.99) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (198.46,265.68) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (202.19,246.83) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (205.93,256.19) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.07,236.95) --
	(209.66,236.95);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (192.86,297.24) {34\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (213.39,  0.00) --
	(213.39,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (217.12,166.67) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (220.85,147.39) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (224.58,147.20) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (228.31,150.68) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (232.05,161.99) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (235.78,151.74) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (239.51,170.65) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (243.24,155.66) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (246.97,179.55) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (217.12,159.38) --
	(250.70,159.38);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (233.91,297.24) {13\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (254.44,  0.00) --
	(254.44,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (258.17,167.17) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (261.90,139.53) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (265.63,141.49) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (269.36,140.86) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (273.09,152.88) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (276.82,131.96) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (280.56,147.94) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (284.29,149.69) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (288.02,156.57) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (258.17,147.85) --
	(291.75,147.85);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (274.96,297.24) {19\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (295.48,  0.00) --
	(295.48,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (299.21,164.07) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (302.95,125.97) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (306.68,129.45) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (310.41,129.08) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (314.14,140.95) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (317.87,118.44) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (321.60,121.35) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (325.34,136.49) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (329.07,144.64) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (299.21,135.00) --
	(332.80,135.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (316.01,297.24) {24\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (336.53,  0.00) --
	(336.53,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (340.26,216.42) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (343.99,235.48) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (347.72,222.58) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (351.46,228.09) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (355.19,229.31) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (358.92,233.69) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (362.65,265.46) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (366.38,249.84) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (370.11,260.21) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (340.26,238.62) --
	(373.85,238.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (357.05,297.24) {35\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (377.58,  0.00) --
	(377.58,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (381.31,218.13) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (385.04,228.31) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (388.77,220.20) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (392.50,226.36) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (396.23,229.72) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (399.97,231.76) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (403.70,254.94) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (407.43,240.20) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (411.16,228.85) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (381.31,231.25) --
	(414.89,231.25);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (398.10,297.24) {30\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (418.62,  0.00) --
	(418.62,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (422.36,214.96) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (426.09,222.09) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (429.82,212.46) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (433.55,222.04) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (437.28,225.80) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (441.01,224.41) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (444.74,244.63) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (448.48,226.72) circle (  2.25);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (452.21,222.15) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (422.36,224.13) --
	(455.94,224.13);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (439.15,297.24) {25\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (459.67,  0.00) --
	(459.67,357.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 69.72, 61.20) -- ( 69.72, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.77, 61.20) -- (110.77, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.82, 61.20) -- (151.82, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.86, 61.20) -- (192.86, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.91, 61.20) -- (233.91, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.96, 61.20) -- (274.96, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.01, 61.20) -- (316.01, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.05, 61.20) -- (357.05, 55.20);
